Excuse me, do you have a moment to talk about version control?

### 2017-10-05 README.Rmd
Make 2 sentences into 1

A lone ranger, working on a single computer, can benefit from adopting version 
control. But not nearly enough to justify the pain of installation and workflow 
upheaval. There are much easier ways to get versioned back ups of files, if 
that's all you're worried about.

>>>>

A lone ranger, working on a single computer, can benefit from adopting version 
control, But not nearly enough to justify the pain of installation and workflow 
upheaval. There are much easier ways to get versioned back ups of files, if 
that's all you're worried about.
